---
title: "Find historical milestones from cited references"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{milestones}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CRMilestones)
```

### Motivation

Intro text, motivation, context, links to references.

### CRExplorer

This package uses CRExplorer, which is free and available from https://andreas-thor.github.io/cre/. A manual to the software can be found here: https://andreas-thor.github.io/cre/manual.pdf.

To use this package, you need a copy of CRExplorer. One is bundled in the package (version 1.9, downloaded in June/2021) and is the default option. If you want to use your own installation, you'll need to pass the path to the function calls below.

### Optogenetics

Example data, maybe redo the search from their paper?
Below it's run with default arguments, but you can change them.
```{r}
wos_records = system.file("extdata", "optogenetics.txt", package = "CRMilestones", mustWork = T)
CR_data = run_CRE(data_files = wos_records)
```

It returns the graph CSV, as a data frame and the list of references, already disambiguated, as a data frame (optionally, it should save the files in CSV or WOS) and the RPYS plot (like the one in the software)
Explain what data is returned, already de-trended

Now you just run the analysis to identify the peak years and references (Tukey HSD?)
```{r}
milestones = identify_milestones(CR_data, n_milestones = 10, n_refs = 1)
```

Returns then a list of milestone references, the list of peak years and the RPYS plot, but indicating peaks with vertical lines and it's done.
```{r}
head(milestones$pubs)
```

```{r}
milestones$graph
```

