---
title: "Find historical milestones from cited references"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{milestones}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CRMilestones)
```

Intro text, motivation, context, links to references.

This package uses CRExplorer, which is free and available from ... . Credits, link to references, manual

First of all, you should install it. If you haven't, run the code below and follow the instructions:
```{r}
install_CRE()
```

Once installed, you'll need to tell the functions where to find it:
```{r}
CREXPLORER_PATH = "..."
```

Example data, maybe redo the search from their paper?
```{r}
CR_data = run_CRE(data_path = "...", cre_path = CREXPLORER_PATH,
                  other_args_to_pass_to_CRExplorer)
```

It returns the CSV, read, as a data frame and the list of references, already disambiguated, as a data frame (optionally, it should save the files in CSV or WOS)
Explain what data is returned, already de-trended

Now you just run the analysis to identify the peak years and references (Tukey HSD?)
```{r}
milestones = identify_milestones(CR_data, n_milestones = 10, n_refs = 1)
```

Returns then a list of references, the list of peak years, the RPYS plots (like the one in the software, but indicating peaks with arrows?) and it's done.
```{r}
head(milestones$pubs)
```

```{r}
milestones$graph
```

